Supplement A to 'Researchers understand and use the logic of significance testing in a novel statistical reasoning task

### 2020-08-15 inst/manuscript/manuscript.Rmd
fixed issues with compilations in updated dependencies

glm_pars_x = broom::tidy(glm_obj_x)
glm_anova_x = broom::tidy(anova(glm_obj_x, test = "Chisq"))
glm_apa_x = papaja::apa_print.glm(glm_obj_x)

pred_p = outer(c(3,7), c(3,7), function(true, z_calc){
  plogis(predict.glm(glm_obj_x, 
              newdata = list(ev = MoreyHoekstra2019:::evz(qnorm(1 - pval / 2), z_calc), 
                 evidence_power = true)
              )
  )
})
dimnames(pred_p) <- list("true"=c("Wide (3)","Narrow (7)"),
                         "z_calc"=c("Wide (3)","Narrow (7)"))

@@

glm_pars_p = broom::tidy(glm_obj_p)
glm_anova_p = broom::tidy(anova(glm_obj_p, test = "Chisq"))
glm_apa_p = papaja::apa_print.glm(glm_obj_p)

>>>>

glm_pars_x = broom::tidy(glm_obj_x)
glm_anova_x = broom::tidy(anova(glm_obj_x, test = "Chisq"))
glm_apa_x = papaja::apa_print(glm_obj_x)

pred_p = outer(c(3,7), c(3,7), function(true, z_calc){
  plogis(predict(glm_obj_x, 
              newdata = list(ev = MoreyHoekstra2019:::evz(qnorm(1 - pval / 2), z_calc), 
                 evidence_power = true)
              )
  )
})
dimnames(pred_p) <- list("true"=c("Wide (3)","Narrow (7)"),
                         "z_calc"=c("Wide (3)","Narrow (7)"))

@@

glm_pars_p = broom::tidy(glm_obj_p)
glm_anova_p = broom::tidy(anova(glm_obj_p, test = "Chisq"))
glm_apa_p = papaja::apa_print(glm_obj_p)

### 2020-08-15 inst/manuscript/supplementA.Rmd
fixed issues with compilations in updated dependencies

Participants also made use of "replications" of the fictional experiments. (Figure B above) shows the distribution of the number of experiments sampled as a function of the true effect size. Median numbers of experiments range from 20 when Jinglies and Sparklies were equally fast, down to 9 when the true effect size was $\delta=1$ and thus the effect was relatively easy to detect (`r papaja::apa_print(kt_expt)$statistic`). When the effect size is small and difficult to detect, participants do more experimentation before deciding.

>>>>

Participants also made use of "replications" of the fictional experiments. (Figure B above) shows the distribution of the number of experiments sampled as a function of the true effect size. Median numbers of experiments range from 20 when Jinglies and Sparklies were equally fast, down to 9 when the true effect size was $\delta=1$ and thus the effect was relatively easy to detect (`r papaja:::apa_print.htest(kt_expt)$statistic`). When the effect size is small and difficult to detect, participants do more experimentation before deciding.
